What is an Ancestral Recombination Graph?

### 2022-03-18 paper.tex

\node [nodelabel,anchor=north west] at ($(s3) + (0,0)$) {$x$};
\foreach \u/\lab in {s0/0, s1/1, s2/2} \node[nodelabel,anchor=north] at (\u) {\lab};
\foreach \u/\lab in {s4/4} \node[nodelabel,anchor=south west] at (\u) {\lab};
\foreach \u/\lab in {s5/5} \node[nodelabel,anchor=south east] at (\u) {\lab};
\foreach \u/\lab in {s3/3, s6/6} \node[nodelabel,anchor=south] at (\u) {\lab};

@@

\node [nodelabel,anchor=north west] at ($(-8.5,5)$) {
\begin{tabular}{c|c}
% \multicolumn{2}{c}{Breakpoint}\\
node & breakpoint\\
\hline
0 & $\varnothing$ \\
1 & $\varnothing$ \\
2 & $\varnothing$ \\
3 & $x$ \\
4 & $\varnothing$ \\
5 & $\varnothing$ \\
6 & $\varnothing$ \\
\end{tabular}};

\node [nodelabel,anchor=north west] at ($(-2.5,5)$) {
\begin{tabular}{l}
Edges\\
\hline
$(0, 4)$ \\
$(1, 3)$ \\
$(2, 5)$ \\
$(3, 4)$ \\
$(3, 5)$ \\
$(4, 6)$ \\
$(5, 6)$ \\
\end{tabular}};

\node [nodelabel,anchor=north west] at ($(6,5)$) {
\begin{tabular}{ll}
Edges\\
\hline
$(0, 4)$ & $(0, L]$ \\
$(1, 3)$ & $(0, L]$ \\
$(2, 5)$ & $(0, L]$ \\
$(3, 4)$ & $(0, x]$ \\
$(3, 5)$ & $(x, L]$ \\
$(4, 6)$ & $(0, L]$ \\
$(5, 6)$ & $(0, L]$ \\
\end{tabular}};

>>>>

\node [nodelabel,anchor=north west] at ($(s3) + (0,0)$) {$x$};
\foreach \u/\lab in {s0/$\textsf{A}$, s1/$\textsf{B}$, s2/$\textsf{C}$} \node[nodelabel,anchor=north] at (\u) {\lab};
\foreach \u/\lab in {s4/$\textsf{E}$} \node[nodelabel,anchor=south west] at (\u) {\lab};
\foreach \u/\lab in {s5/$\textsf{F}$} \node[nodelabel,anchor=south east] at (\u) {\lab};
\foreach \u/\lab in {s3/$\textsf{D}$, s6/$\textsf{G}$} \node[nodelabel,anchor=south] at (\u) {\lab};

@@

\node [nodelabel,anchor=north west] at ($(-10,5)$) {
\begin{tabular}{c|c}
% \multicolumn{2}{c}{Breakpoint}\\
node & breakpoint\\
\hline
$\textsf{A}$ & $\varnothing$ \\
$\textsf{B}$ & $\varnothing$ \\
$\textsf{C}$ & $\varnothing$ \\
$\textsf{D}$ & $x$ \\
$\textsf{E}$ & $\varnothing$ \\
$\textsf{F}$ & $\varnothing$ \\
$\textsf{G}$ & $\varnothing$ \\
\end{tabular}};

\node [nodelabel,anchor=north west] at ($(-4,5)$) {
\begin{tabular}{l}
Edges\\
\hline
$(\textsf{A}, \textsf{E})$ \\
$(\textsf{B}, \textsf{D})$ \\
$(\textsf{C}, \textsf{F})$ \\
$(\textsf{D}, \textsf{E})$ \\
$(\textsf{D}, \textsf{F})$ \\
$(\textsf{E}, \textsf{G})$ \\
$(\textsf{F}, \textsf{G})$ \\
\end{tabular}};

\node [nodelabel,anchor=north west] at ($(7,5)$) {
\begin{tabular}{ll}
Edges\\
\hline
$(\textsf{A}, \textsf{E})$ & $(0, L]$ \\
$(\textsf{B}, \textsf{D})$ & $(0, L]$ \\
$(\textsf{C}, \textsf{F})$ & $(0, L]$ \\
$(\textsf{D}, \textsf{E})$ & $(0, x]$ \\
$(\textsf{D}, \textsf{F})$ & $(x, L]$ \\
$(\textsf{E}, \textsf{G})$ & $(0, L]$ \\
$(\textsf{F}, \textsf{G})$ & $(0, L]$ \\
\end{tabular}};
